### 2014-03-19 paper/exampleobjects.tex

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/brain.png}
\caption{A touch-sensitive brain whose tubes are filled with conductive paint.  Sensing is done on a single wire via SFCS.  Inset shows the internal structure of the tubes generated by our design tool.}
\label{fig:toys}
\end{figure}

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/bunny.png}
\caption{This rabbit has an open tube leading to its mouth and a semi-closed tube capped with flexible material in its back.  When air is sucked in through the open tube, the back becomes stiff as though the rabbit has breathed in.  Inset shows the interior structure.}
\label{fig:breathe}
\end{figure}

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/radio.png}
\caption{This radio is assembled from traditional electronic components connected by copper-filled tubes.  The case was designed to allow the components to recess into it slightly.  Inset shows the internal structure of the tubes generated by our design tool.}
\label{fig:radio}
\end{figure}

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/pens.png}
\caption{This pen holder uses the FlyEye technique to sense the presence or absence of an object in each of its tubes.  Inset shows the internal structure of the tubes generated by our design tool.}
\label{fig:pens}
\end{figure}

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/maze.png}
\caption{Our maze game has a large single particle trapped inside a fully enclosed tube.  It offers hours of fun!}
\label{fig:maze}
\end{figure}

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/sign.png}
\caption{A two-state animated neon sign designed using our tool (a)(b) \valkyrie{Tovi: we could use your PDF hax to make this animate in place :)}.  (c) shows the SVG input files to create this sign, and (d) shows an isometric view of the tubes created by our tool.}
\label{fig:neon}
\end{figure}

>>>>

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/placeholder/brain.jpg}
\caption{A touch-sensitive brain whose tubes are filled with conductive paint.  Sensing is done on a single wire via SFCS.  Inset shows the internal structure of the tubes generated by our design tool.}
\label{fig:toys}
\end{figure}

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/placeholder/bunny.jpg}
\caption{This rabbit has an open tube leading to its mouth and a semi-closed tube capped with flexible material in its back.  When air is sucked in through the open tube, the back becomes stiff as though the rabbit has breathed in.  Inset shows the interior structure.}
\label{fig:breathe}
\end{figure}

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/placeholder/radio.jpg}
\caption{This radio is assembled from traditional electronic components connected by copper-filled tubes.  The case was designed to allow the components to recess into it slightly.  Inset shows the internal structure of the tubes generated by our design tool.}
\label{fig:radio}
\end{figure}

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/placeholder/pens.jpg}
\caption{This pen holder uses the FlyEye technique to sense the presence or absence of an object in each of its tubes.  Inset shows the internal structure of the tubes generated by our design tool.}
\label{fig:pens}
\end{figure}

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/placeholder/maze.jpg}
\caption{Our maze game has a large single particle trapped inside a fully enclosed tube.  It offers hours of fun!}
\label{fig:maze}
\end{figure}

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/placeholder/sign.jpg}
\caption{A two-state animated neon sign designed using our tool (a)(b) \valkyrie{Tovi: we could use your PDF hax to make this animate in place :)}.  (c) shows the SVG input files to create this sign, and (d) shows an isometric view of the tubes created by our tool. \valkyrie{d) is a lot less interesting if we are making planar tubes.  also, for c, should we show an overlay of the two states?  maybe in different colors?}}
\label{fig:neon}
\end{figure}

### 2014-03-19 paper/introduction.tex

\section{Introduction}
Redirection leads to reusable and iterable devices.  Televisions have long been operating on this idea: before the recent switch to digital television signals, TV signals had remained unchanged since roughly the 1920s, and the only requirement to bigger and better viewing was an upgrade of the \emph{endpoint itself}.  A larger television does not require an upgrade of the underlying broadcast system.  Similarly, the Internet, famously described by US Senator Ted Stephens (R-Alaska) as a ``series of tubes'', works on the principle of routing and distributing information to endpoints; there is no need to reduplicate information in multiple locations as long as it can be retrieved and manipulated by users at their laptops, tablets, mobile phones, or swarm devices.

@@

Willis, et al., ``envision a future world where interactive devices can be printed rather than assembled; a world where a device with active components is created as a single object, rather than a case enclosing circuit boards and individually assembled parts" \cite{Willis-printedoptics}.  This is a vision we eagerly share: 3D printers are capable of creating arbitrary geometries not feasible to manufacture using traditional processes, and makers and designers are underutilizing these capabilities.

In this paper, we propose a new technique in which interior hollow chambers and pipes are integrated into 3D printed devices to redirect interactive components from a central system to arbitrary points on a printed object's surface. Such channels introduce an entire design space of opportunities for adding interactivity to these objects. For example, copper material can fill the channels, to allow for standard electronic components to be easily integrated after the printout; air can be pumped through to create tactile output; or electroluminescent wire can be threaded through to create computer-controlled visual output.

@@

\begin{itemize}
\item We lay out a design space of tube-mediated interactive possibilities. 
\item We offer algorithms and techniques for routing tubes, as well as a design tool implementing them.
\item We showcase a set of examples, enabled by our modeling tool and exploring new points in the design space.
\end{itemize}

>>>>

\section{Introduction}

\bjoern{I liked the first sentence of the older intro: ``Makers, as well as professional designers, leverage 3D printers as tools for design work.  A wide array of objects, ranging from bicycle helmets to jewelry to video game controllers, are now prototyped or even manufactured using these machines.  However, most devices fabricated by 3D printers are passive.''}

Redirection leads to reusable and iterable devices.  Televisions have long been operating on this idea: before the recent switch to digital television signals, TV signals had remained unchanged since roughly the 1920s, and the only requirement to bigger and better viewing was an upgrade of the \emph{endpoint itself}.  A larger television does not require an upgrade of the underlying broadcast system.  Similarly, the Internet, famously described by US Senator Ted Stephens (R-Alaska) as a ``series of tubes'', works on the principle of routing and distributing information to endpoints; there is no need to reduplicate information in multiple locations as long as it can be retrieved and manipulated by users at their laptops, tablets, mobile phones, or swarm devices. \bjoern{Not sure this works as an introduction. The first sentence requires a lot of explanation before the reader understands what you mean by ``redirection'' or ``reuse'' or ``iterable''. I don't follow the TV example.}

@@

Willis, et al., ``envision a future world where interactive devices can be printed rather than assembled; a world where a device with active components is created as a single object, rather than a case enclosing circuit boards and individually assembled parts" \cite{Willis-printedoptics}.  This is a vision we eagerly share: 3D printers are capable of creating arbitrary geometries not feasible to manufacture using traditional processes, and makers and designers are underutilizing these capabilities.
\bjoern{I think we're doing something a little different from Karl's vision - in all of our examples, you need to hook up extra sensors, actuators, or lights to the 3D-printed object. So there's always still assembly required. We're not really printing interactive objects in a single pass, but we're offering new ways of adding interactivity to 3D printed objects.

I'd argue the principal novelty of our work is to {\em remove material} from a model to form pipes and other cavities. We demonstrate how designers/makers can then use these pipes, e.g. by filling them with various media to enable input, display and tactile feedback. This {\em subtractive} approach is complementary to {\em additive} approaches that try to print different materials such as conductors. While our approach requires manual assembly afterwards, it opens up a large useful design space on commonly available 3D printers.

It's a useful insight that many of our approaches work by ``redirection'' (but not all - EL wire???). But I'd mention it as a sub-point here, not as the driving story.}

In this paper, we propose a new technique in which interior hollow chambers and pipes are integrated into 3D printed devices to redirect interactive components from a central system to arbitrary points on a printed object's surface. Such channels introduce an entire design space of opportunities for adding interactivity to these objects. For example, copper material can fill the channels, to allow for standard electronic components to be easily integrated after the printout; air can be pumped through to create tactile output; or electroluminescent wire can be threaded through to create computer-controlled visual output.\bjoern{this is good - I'd make this the central argument of the intro and move it up earlier.}

@@

\begin{itemize}
\item We lay out a design space of tube-mediated interactive possibilities. 
\item We offer algorithms and techniques for routing tubes, as well as a design tool implementing them.
\item We showcase a set of examples, enabled by our modeling tool and exploring new points in the design space.
\end{itemize}
\bjoern{I'd say more about the software contribution in the abstract. Maybe that just requires expanding these bullets into a full paragraph.}
